Reference label transfer of the fetal kidney reference (Stewart et al.) for `r params$sample_id`

### 2024-08-29 analyses/cell-type-wilms-tumor-06/notebook_template/02a_label-transfer_fetal_full_reference_Cao.Rmd
Try debug RunAzimuth

if(dim(srat)[2] < 100){
 s <- RunAzimuth_small(srat, reference ="fetusref", k.weight = 10, mapping.score.k = 80, ksmooth = 80)
} else {
 s <- RunAzimuth(srat, reference ="fetusref")

>>>>

print(dim(srat)[2])
# this would need to be change for CI or whole sample
 s <- RunAzimuth_small(srat, reference ="fetusref", k.weight = 10, mapping.score.k = 80, ksmooth = 80)

### 2024-08-29 analyses/cell-type-wilms-tumor-06/notebook_template/02b_label-transfer_fetal_kidney_reference_Stewart.Rmd
Try debug RunAzimuth

if(dim(srat)[2] < 500){
 s <- RunAzimuth_small(srat, reference =path_to_reference, assay = 'RNA',k.weight = 10, mapping.score.k = 80, ksmooth = 80)
} else {
 s <- RunAzimuth(srat, reference =path_to_reference,assay = 'RNA' )

}
print(dim(srat)[2])

>>>>

# this would need to be change for CI or whole sample
 s <- RunAzimuth_small(srat, reference =path_to_reference, assay = 'RNA',k.weight = 10, mapping.score.k = 80, ksmooth = 80)
